Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-15 paper/main.tex
Added discussion of truncating and different platforms

>>>>

\subsection{Truncate output from 512-bit implementations}
In our measurements and Python library we only consider 256-bit version of each
candidate. Some candidates does however have a faster implementation with
512-bit output. We could have used these implementations and truncated the
output to 256-bit, and possible achieved better results.

\subsection{Testing on difference architectures}
Our measurements are only done on a single computer with an 32-bit (x86)
system. It would have been possible to extend the survey to other
architectures, to see how this would affect the results.
